Probing internal structure of distant quasars using Microlensing

### 2014-04-15 paper1/intro.tex
first correction intro.tex

According to the paradigm, the object is powered through the accretion of matter from the proximal environment into the black hole. The radiation emitted excites the surrounding medium which becomes detectable as the narrow line regions,
broad band regions and torus. Moreover, in the direction perpendicular to the accretion disk, where the medium is more transparent, jets will appear. When the medium between and observer and such an object is transparent due to the observation direction  
a quasar can be observed (citation). In other words an active galactic nucleus (AGN) with one of the poles orientated towards Earth would be detected as a quasar by an observer. \\

Through extensive observations done in the past 50 years, an important part of the assumptions and details  regarding the mechanism have been confirmed and uncovered. Still, the black hole shadow and the surrounding luminous accreting material (the black hole silouette) remains to be probed. Advancements in the very long baseline interferometer observations have made possible since 2007, the detection of structures of a few Schwarzschild radii at the Sagitarius A object at the center of our galaxy \citep{2008JPhCS.131a2055D}. Furthermore, jet launching structure near the supermasve black hole in M87 were resolved with the same observation tool \citep{2012Sci...338..355D}. With all the advancement, the current number of baselines does not allow the direct creation of images from the observations still it does allow the fitting of the data to predefined models \citep{2013MNRAS.434..765K}.

@@

Hundreds of thousands of quasars have been detected up to date, mainly from the Sloan Digital Sky Survey. The great majority of them present a redshift larger than 2.15 of their spectra (Paris et al 20Nov 2013 SDSS catalogue). Therefore the typical distance to the objects is in the order of Gigaparsecs (Gpc) or above. A value that is orders of magnitude 
larger than the distance to M87, estimated to be 50 Mpc? (citation). Direct observation of the black hole silouette of quasars require significant technological advances. We argue in the present paper
 that one can probe and study the black hole shadow and its proximal environment belonging to a quasar without having to resolve sub-event horizon scales. We consider that this is possible by analyzing the data from microlensing-events.  Moreover, unlike with the few nearby AGNs, the study of the very large quasar population allows for the statistical refinement of the global properties of AGN by highlighting any particular
characteristic that is present only in SGA* and M87 central region. Furthermore, by probing the event-horizon-scale inner regions of of a large number of objects will facilitate the study of the evolution of the previously mentioned region.

@@

In the third section we introduce the three source profiles used in our models and simulations. We start with two commonly used and simple sources. Namely the gaussian brightness distribution and constant intensity disk. In addition we use a geometric crescent-shaped source effectively the same as the one introduced by \citep{2013MNRAS.434..765K} with constant surface brightness. \\
The fourth section contains the results of our simplified models calculations, including the numerical equation for lightcurve calculations and the corresponding plots. In order to facilitate comparison bewteen the lightcurves of the three distinct sources, we constrain the luminosity and half-light radius of all sources to have the same value.

>>>>

According to the paradigm, the object is powered through the accretion of matter from the proximal environment into the black hole. The radiation emitted excites the surrounding medium which becomes detectable as the narrow line regions,
broad band regions and torus. Moreover, in the direction perpendicular to the accretion disk, where the medium is more transparent, jets will appear. When the medium between and observer and such an object is transparent a quasar can be observed (citation). In other words an active galactic nucleus (AGN) with one of the poles orientated towards Earth would be detected as a quasar by an observer. \\

Through extensive observations done in the past 50 years, an important part of the assumptions and details  regarding the mechanism have been confirmed and uncovered. Still, the black hole shadow and the surrounding luminous accreting material (the black hole silouette) remains to be probed. Advancements in the very long baseline interferometer observations have made possible since 2007, the detection of structures of a few Schwarzschild radii at the Sagitarius A object at the center of our galaxy \citep{2008JPhCS.131a2055D}. Furthermore, jet launching structure near the supermasve black hole in M87 were resolved with the same observation tool \citep{2012Sci...338..355D}. With all the advancement, the current number of baselines does not allow the direct generation of images from the observations still it does allow the fitting of the data to predefined models \citep{2013MNRAS.434..765K}.

@@

Hundreds of thousands of quasars have been detected up to date, mainly from the Sloan Digital Sky Survey. The great majority of them present a redshift larger than 2.15 of their spectra (Paris et al 20Nov 2013 SDSS catalogue). Therefore the typical distance to the objects is in the order of gigaparsecs  or above. A value that is orders of magnitude larger than the distance to M87. Direct observation of the black hole silouette of quasars require significant technological advances. We argue in the present paper
 that one can probe and study the black hole shadow and its proximal environment belonging to a quasar without having to resolve sub-event horizon scales. We consider that this is possible by analyzing the data from microlensing-events.  Moreover, unlike with the few nearby AGNs, the study of the very large quasar population allows for the statistical refinement of the global properties of AGN by highlighting any particular
characteristic that is present only in SGA* and M87 central region. Furthermore, by probing the event-horizon-scale inner regions of a large number of objects will facilitate the study of the evolution of the previously mentioned region.

@@

In the third section we introduce the three source profiles used in our models and simulations. We start with two commonly used and simple sources. Namely the gaussian brightness distribution and the constant intensity disk. In addition we use a geometric crescent-shaped source effectively the same as the one introduced by \citep{2013MNRAS.434..765K} with constant surface brightness. \\
The fourth section contains the results of our simplified models calculations, including the numerical equation for lightcurve calculations and the corresponding plots. In order to facilitate comparison bewteen the lightcurves of the three distinct sources, we constrain the luminosity and half-light radius of all sources to have the same value.
